make STEAM clear

### 2019-12-11 mstemc/index.tex
an important commit: the drawing in tikz post works well

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Drawing Graphs Using TikZ in Emacs Org}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Drawing Graphs Using TikZ in Emacs Org},
 pdfkeywords={},
 pdfsubject={This post collects working examples of drawing graphs using TikZ in Emacs Org},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Drawing Graphs Using TikZ in Emacs Org}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Drawing Graphs Using TikZ in Emacs Org},
 pdfkeywords={},
 pdfsubject={This post collects working examples of drawing graphs using TikZ in Emacs Org},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

Draw a graph using TikZ

[[file:~/Dropbox/mstemc_hugo/static/img/tikz/example.pdf]]

### 2019-12-11 mstemc/mstemc.tex
an important commit: the drawing in tikz post works well

% Intended LaTeX compiler: xelatex
\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{make STEAM clear}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={make STEAM clear},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Videos}
\label{sec:org002a437}

\section{Posts}
\label{sec:org2d95323}

\subsection{Set up the TikZ in Emacs Org File}
\label{sec:org64c90ff}
\begin{summary}
Why is this in \textbf{green}?
\end{summary}

\subsubsection{config the header args}
\label{sec:org825d7de}

@@

\begin{verbatim}
#+name: tutorial
#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
#+header: :results raw :exports none :fit yes :border 0cm
#+header: :imagemagick t :iminoptions -density 400 :imoutoptions -geometry 400 -flatten
#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning, shapes.symbols, calc}")
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src
#+RESULTS: tutorial
[[file:../../img/tikz/tutorial.png]]
\end{verbatim}

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\subsubsection{generate results with different formats}
\label{sec:org75935d2}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\subsubsection{export the results according to the backend}
\label{sec:org59da2c2}

@@

\subsubsection{the final workflow}
\label{sec:orgc0cd8cc}

@@

\section{Projects}
\label{sec:org8f61cb8}

\subsection{my workflow of creating a video}
\label{sec:org597f5bb}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:org76d34e1}

@@

\begin{enumerate}
\item program and debug
\label{sec:orgd2ab070}

@@

\item Org mode - journalize your work
\label{sec:org75ff6e1}

@@

\item Org mode - get things done
\label{sec:org4df4183}

\item Org mode - write a diary
\label{sec:org266bdcc}

\item Org mode - export your Org file
\label{sec:orge9ee370}

\item program and debug
\label{sec:orgcf10226}

\item writing latex
\label{sec:org69631c2}
\item org-journal
\label{sec:org06a8ebe}

@@

\item ox-hugo
\label{sec:orgde97df4}

@@

\item preview tikz picture in Org
\label{sec:org2bcb08b}

@@

\subsubsection{Hugo}
\label{sec:org79f095e}

@@

I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
about how to leverage Hugo. Ox-hugo helps me do most of the work.

\subsubsection{manim}
\label{sec:orga490cc3}

\subsubsection{blender}
\label{sec:org362635d}

\section{Courses}
\label{sec:orgc9e6ff6}
\end{document}

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue,palatino]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{make STEAM clear}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={make STEAM clear},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Videos}
\label{sec:org80ec581}

\section{Posts}
\label{sec:org275e087}

\subsection{Set up the TikZ in Emacs Org}
\label{sec:org5387454}
\hspace{0pt}\\

An introduction to setup the TikZ environment in Emacs Org File. So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.

\subsubsection{config the header args}
\label{sec:org3f3612a}

@@

\begin{verbatim}
#+name: tutorial
#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
#+header: :results raw :exports none :fit yes :border 0cm
#+header: :imagemagick t :iminoptions -density 400
#+header: :imoutoptions -geometry 400 -flatten
#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
           shapes.symbols, calc}")
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src
#+RESULTS: tutorial
[[file:../../img/tikz/tutorial.png]]
\end{verbatim}

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\subsubsection{generate results with different formats}
\label{sec:orgac277d3}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\subsubsection{export the results according to the backend}
\label{sec:org864fe62}

@@

\subsubsection{the final workflow}
\label{sec:orgc26c788}

@@

\subsection{Export Markdown and latex using Emacs Org}
\label{sec:orgb25f912}

\hspace{0pt}\\

set up the Emacs org and ox-hugo to export the org files in markdown and latex format.

\subsubsection{Introduction}
\label{sec:org1a16d6f}

I use hugo before it support Emacs org file. Then I use an Emacs extension
called \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} which is a carefully crafted Org exporter back-end for Hugo.
Ox-hugo meets all my requirement and definitely worth a try when you are an
advanced user of Emacs Org. By the way, if you are quite familiar with Emacs
Org, there is no need to take time to learn markdown. Emacs Org, I think, is
more elegant than markdown.

\subsubsection{set up ox-hugo}
\label{sec:org11a7de8}

I use Spacemacs and integrate ox-hugo into my config is easy. You can add it
into your private layer or just add it in your \texttt{user-config} . Please refer to
\href{https://github.com/kaushalmodi/ox-hugo}{the repo.} and read the document for more information.

The first time you want to export an Org file or a subtree of an Org file, use
\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
\subsubsection{use Org Macro replacement}
\label{sec:orgf79a086}

Often, you want different actions when you export the Org file to
hugo-compatible markdown and latex file. For example, hugo or hugo theme supports
summary and shortcodes such as \texttt{alert note} and \texttt{alert warning} (see  \href{https://sourcethemes.com/academic/docs/writing-markdown-latex/}{Writing
content with Markdown, \LaTeX{}, and Shortcodes | Academic} )

When you export the snippet to markdown then hugo will display the content
according to the css. However, latex does not recognize the shortcodes. So latex
will display \texttt{\{ \{\% alert note \%\} \}} literally which is clutter. The Org Macro may
help. For more information please refer to \href{https://orgmode.org/manual/Macro-replacement.html}{The Org Manual: Macro replacement} and
\href{https://github.com/fniessen/org-macros}{fniessen/org-macros: Shared macros for Org mode} . I also define my own Org Macro
in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setup file for every .org file}. With Org Macro, I control some contents
and options exist only for certain backend.

Once you are familiar with Org Macro, It behaves beyond your imagination.
\subsubsection{use the setupfile for each Org file}
\label{sec:org66edc24}

Often, you options for a org file grows more and more. If you think it kind of
clutter at the top of your Org files, you can group them in a setupfile then
include it at the top of your Org file.

For my setupfiles, please refer to \href{https://github.com/msteamc/.spacemacs.d/tree/master/org-templates}{my org-templates}. As you can see, I have
several setupfiles for different aims. To include one of them in my Org file, I
use:

\texttt{\#+SETUPFILE: <path+name of the setup files>}

By using \texttt{\#+SETUPFILE} ,I only have to option lines at the top of my org file.
So it looks clean.

Also, you can notice that in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setupfile named enpost.org} exists options for
different export targets.

\subsection{Drawing Graphs Using TikZ in Emacs Org}
\label{sec:org171ea2a}

Draw a graph using TikZ

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
\end{center}

\section{Projects}
\label{sec:org91fe676}

\subsection{my workflow of creating a video}
\label{sec:org7aa4f8b}
\hspace{0pt}\\

This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.

During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:org2fbd9b9}

@@

\begin{enumerate}
\item program and debug
\label{sec:org2090515}

@@

\item Org mode - journalize your work
\label{sec:org68fd51b}

@@

\item Org mode - get things done
\label{sec:orgc649c82}

\item Org mode - write a diary
\label{sec:orgc5ee9f2}

\item Org mode - export your Org file
\label{sec:orgec750d0}

\item program and debug
\label{sec:org78ee2a9}

\item writing latex
\label{sec:org5309ad9}
\item org-journal
\label{sec:orgb4dcd6b}

@@

\item ox-hugo
\label{sec:org5a96636}

@@

\item preview tikz picture in Org
\label{sec:org8bf8be5}

@@

\subsubsection{Hugo}
\label{sec:orgaed3855}

@@

I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
about how to leverage Hugo. Ox-hugo helps me do most of the work.
\subsubsection{Hugo Academic Theme}
\label{sec:org7ca124e}

\href{https://github.com/gcushen/hugo-academic}{Hugo Academic Theme} is a beautiful and flexible theme developed for Hugo. This
site is built based on this theme.

If you want attach a pdf version of your post, two steps are needed:
\begin{enumerate}
\item add a line:
\begin{verbatim}
url_pdf = "#"
\end{verbatim}
in the front matter of your markdown file.
\item add a PDF file with the same name as your post’s own folder to your post’s
folder.
\end{enumerate}

A PDF link will be automatically generated just like the \texttt{pdf} link appears in
the top of each post in my site. Because I use Emacs Org with ox-hugo, I add one
line in the property:

\begin{verbatim}
:EXPORT_HUGO_CUSTOM_FRONT_MATTER+: :url_pdf "#"
\end{verbatim}

Hugo academic theme provide some front matters that hugo does not support by
default. Fortunately, \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} handles this effectively. For more information.
you can read:
\begin{enumerate}
\item \href{https://ox-hugo.scripter.co/doc/org-meta-data-to-hugo-front-matter/}{Org meta-data to Hugo front-matter}
\item \href{https://ox-hugo.scripter.co/doc/custom-front-matter/}{Custom Front-matter Parameters}
\end{enumerate}

\subsubsection{manim}
\label{sec:org12e9ea1}

\subsubsection{blender}
\label{sec:orgb3042c1}

\section{Courses}
\label{sec:org92abef5}
\end{document}
